### 2017-01-03 paper/evaluation.tex
pass on rq2

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features in build
files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

@@

To evaluate the  use of low-level parallelism, we considered the 91
subjects from the groups \emph{long} and \emph{medium} identified in
Section~\ref{sec:rqone}. In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. In addition, we are interested in
understanding how these parallel settings are used. Given a list of
subjects, our script searches recursively all \emph{pom.xml} files
from the project directory and uses the command-line tool \emph{grep}
to highlight the presence of the keywords \emph{forkMode},
\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
any possible combination of parallel settings (see
Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
subjects with evidence of parallel settings. After the inspection of
130 configuration files, we confirmed that \Fix{X} settings are real
parallel configurations.  These settings are related to \Fix{Y}
subjects. It is important to notice that, \Fix{X}\% of the subjects
(\emph{medium} and \emph{long} aggregated) did not explore low-level
parallelism according to our criteria of matching keywords. After the
inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
projects doesn't use parallel features, so what?}
Table~\ref{tab:inspection-table} summarizes our initial findings.

>>>>

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How often are parallelization features present in
build files?}
\newcommand{\RQC}{What is the impact of parallalelization?}

@@

To evaluate the presence of parallelization settings, we considered
the \Fix{91} subjects from the groups \emph{long} and \emph{medium}
identified in Section~\ref{sec:rqone}. We focused in these two groups
because they represent costly test suites and are more likely that the
developers may have used strategies to reduce the execution cost (\eg,
running parts of the tests in different threads). We computed the
frequence of the parallelism modes (see Section \ref{sec:modes}) using
a partially manual approach: we first discover automatically the
relevant configuration files and then we manually inspect to eliminate
false-positves (\eg, commented configuration).

\Fix{---------------------}

In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. In addition, we are interested in
understanding how these parallel settings are used. Given a list of
subjects, our script searches recursively all \emph{pom.xml} files
from the project directory and uses the command-line tool \emph{grep}
to highlight the presence of the keywords \emph{forkMode},
\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
any possible combination of parallel settings (see
Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
subjects with evidence of parallel settings. After the inspection of
130 configuration files, we confirmed that \Fix{X} settings are real
parallel configurations.  These settings are related to \Fix{Y}
subjects. It is important to notice that, \Fix{X}\% of the subjects
(\emph{medium} and \emph{long} aggregated) did not explore low-level
parallelism according to our criteria of matching keywords. After the
inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
projects doesn't use parallel features, so what?}
Table~\ref{tab:inspection-table} summarizes our initial findings.
